\textbf{ Interpretable Gaussian Processes for Stellar Variability }

### 2020-12-13 tex/gitlinks.tex
new tests

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/03e335802a72714ed06f39e85f3d9c14193a5e32/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/03e335802a72714ed06f39e85f3d9c14193a5e32/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/03e335802a72714ed06f39e85f3d9c14193a5e32/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/rodluger/starry_process/blob/5781bddaacfcc41fd945fb4973484b36d4d5e68b/tex/tests/#1.py}{\raisebox{-0.1em}{\input{tests/#1.tex}}}}
\newcommand{\cilink}[1]{\href{https://dev.azure.com/rodluger/starry_process/_build}{#1}}
